Prag Bat Summary

### 2020-10-28 analysis/summary.Rmd
playing around with factor analysis

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)

@@

```{r, include=FALSE}
data <- bind_rows(
  read_csv("../data/data_r1.csv")%>%filter(task != "training")%>%mutate(round = "R1"),
  read_csv("../data/data_r2.csv")%>%mutate(round = "R2")
  )%>%
  mutate(round = factor(round),
         id = paste(round, id, sep = "_"))

```{r, include=FALSE}
data%>%
  group_by(subage)%>%
  summarise(n= length(unique(id)))
```
# Objective

@@

```{r}
data %>%
  group_by(subage,id,round)%>%
  summarise(testdays = length(unique(test_day)))%>%
  group_by(round,subage)%>%
  summarise(n = length(unique(id)),
            complete_retest_data = sum(testdays == 2))%>%
  kable()
```

@@

@@

```{r}
p1 <- data%>%
  group_by(round, id,age, subage,task)%>%
  filter(task != "training")%>%
  summarise(mean = mean(correct))

p2 <- p1 %>%
  group_by(round,subage,task)%>%
  tidyboot_mean(column = mean)%>%
  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))

ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
  geom_smooth(data = p1, aes(x = age, y = mean, lty = round), method = "lm", col = "black", size = 1)+
  geom_jitter(data = p1, aes(x = age, y = mean, pch = round), alpha = .5, width = .05, height = .01)+
  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = round), position = position_dodge(width = .5))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  ylim(-0.05, 1.05)+
  theme_few()+
  theme(legend.position = c(.85,.1), legend.direction = "horizontal")

@@

```{r}
reli <- data%>%
  filter(task != "training")%>%
  droplevels()%>%
  group_by(round,id,task, test_day)%>%
  summarise(mean = mean(correct))%>%
  spread(test_day, mean)%>%
  na.omit()%>%
  rename("Day1" = `1`,
         "Day2" = `2`)%>%
  group_by(round,task)%>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value)%>%
  mutate_if(is.numeric, round, digits = 2)

reli%>%
  kable()
```

@@

```{r, fig.align="center"}
cor_r1 <- data%>%
  filter(round == "R1")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli%>%filter(round == "R1")%>%pull(reli))%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(round = "R1")

cor_r2 <- data%>%
  filter(round == "R2")%>%
  droplevels()%>%
  group_by(id,task)%>%
  summarise(mean = mean(correct))%>%
  spread(task, mean)%>%
  ungroup()%>%
  select(-id)%>%
  corrr::correlate(diagonal = reli%>%filter(round == "R2")%>%pull(reli))%>%
  gather(task, cor, -rowname)%>%
  mutate(cor = replace(cor, duplicated(cor), NA))%>%
  mutate_if(is.numeric, round, digits = 2)%>%
  na.omit()%>%
  mutate(round = "R2")

@@

>>>>

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
#library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)
library(lavaan)
```

```{r, include=FALSE}
data <- bind_rows(
  read_csv("../data/data_r1.csv") %>%filter(task != "training") %>%mutate(round = "R1"),
  read_csv("../data/data_r2.csv") %>%mutate(round = "R2")
  ) %>%
  mutate(round = factor(round),
         id = paste(round, id, sep = "_"))

@@

```{r, include=FALSE}
data %>%
  group_by(subage) %>%
  summarise(n= length(unique(id)))
```
# Objective

@@

```{r}
data %>%
  group_by(subage,id,round) %>%
  summarise(testdays = length(unique(test_day))) %>%
  group_by(round,subage) %>%
  summarise(n = length(unique(id)),
            complete_retest_data = sum(testdays == 2)) %>%
  kable()
```

@@

Round 2 included the following tasks:

@@

```{r}
p1 <- data %>%
  group_by(round, id,age, subage,task) %>%
  filter(task != "training") %>%
  summarise(mean = mean(correct))

p2 <- p1 %>%
  group_by(round,subage,task) %>%
  tidyboot_mean(column = mean) %>%
  mutate(chance = ifelse(task == "discourse_continuity", 1/3, 1/2))

ggplot()+
  geom_hline(data = p2, aes(yintercept = chance), lty = 2)+
  geom_smooth(data = p1, aes(x = age, y = mean, lty = round), method = "lm", col = "black", size = 1)+
  geom_jitter(data = p1, aes(x = age, y = mean, pch = round), alpha = .5, width = .05, height = .01)+
  geom_pointrange(data = p2, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage), pch = round), position = position_dodge(width = .5))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct") +
  scale_color_ptol(name = "Age") +
  ylim(-0.05, 1.05)+
  theme_few()+
  theme(legend.position = c(.85,.1), legend.direction = "horizontal")

@@

```{r}
wide_data <- data %>%
  filter(task != "training") %>%
  droplevels() %>%
  group_by(round,id,task, test_day) %>%
  summarise(mean = mean(correct)) %>%
  spread(test_day, mean) %>%
  na.omit() %>%
  rename("Day1" = `1`,
         "Day2" = `2`)

reli <- wide_data %>%
  group_by(round, task) %>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value, 
            n = n()) %>%
  mutate_if(is.numeric, round, digits = 2)

reli %>%
  kable()
```
Explore consolidating across rounds.

```{r}
reli_task <- wide_data %>%
  group_by(task) %>%
  summarize(reli = cor.test(Day1,Day2)$estimate,
            lci = cor.test(Day1,Day2)$conf.int[1],
            uci = cor.test(Day1,Day2)$conf.int[2],
            p = cor.test(Day1,Day2)$p.value, 
            n = n()) %>%
  mutate_if(is.numeric, round, digits = 2)

reli_task %>%
  arrange(desc(reli)) %>%
  kable()
```

@@

```{r, fig.align="center"}
cor_r1 <- data %>%
  filter(round == "R1") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli %>%
                     filter(round == "R1") %>%
                     pull(reli)) %>%
  gather(task, cor, -rowname) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(round = "R1")

cor_r2 <- data%>%
  filter(round == "R2") %>%
  droplevels() %>%
  group_by(id,task) %>%
  summarise(mean = mean(correct)) %>%
  spread(task, mean) %>%
  ungroup() %>%
  select(-id) %>%
  corrr::correlate(diagonal = reli%>%filter(round == "R2") %>%pull(reli)) %>%
  gather(task, cor, -rowname) %>%
  mutate(cor = replace(cor, duplicated(cor), NA)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  na.omit() %>%
  mutate(round = "R2")

@@

# Factor analysis

## EFA

Average across task days.

```{r}
efa_data <- filter(data, round == "R1") %>%
  group_by(id, task) %>% 
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = task, values_from = correct)
```

```{r}
fa_data <- as.matrix(dplyr::select(ungroup(efa_data), -1))
f1 <- factanal(fa_data, 1)
f1
```

```{r}
f2 <- factanal(fa_data, 2)
f2
```
`

## CFA
[https://lavaan.ugent.be/tutorial/cfa.html]()

Data

```{r}
lavaan_data <- filter(data, round == "R1", test_day == 1) %>%
  group_by(id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = task, values_from = correct)
```

```{r}
model1 <- 'pragmatic  =~ informativeness + novelty + preference + mutual_exclusivity 
          ef =~ card_sorting'

fit <- cfa(model1, data=lavaan_data)
summary(fit)
```
